---
title: "p8105_hw1_ah4167"
author: "Aiying Huang"
date: "2023-09-14"
output: github_document
---

# Problem 1

```{r}
library("moderndive")
data("early_january_weather")
```
## Description of the dataset:

* The dataset contains weather-related information of EWR for the year 2013, specifically for the month of January. The variables in this dataset including `r colnames(early_january_weather)`, their descriptions are:

1.origin: This variable is of `r typeof(early_january_weather$origin)` type, indicating the source from which the weather data originates. It appears to be a EWR airport.

2.year: This variable represents the year of the data, which is 2013 in this case. All the data entries in this dataset are from the year 2013.

3.month: The "month" variable denotes the month of the year, which is January in this dataset. The data seems to be limited to January 2013.

4.day: This variable represents the day of the month, whose range is `r range(early_january_weather$day)`. It indicates the specific day within January 2013.

5.hour: The "hour" variable represents the hour of the day, whose range is `r range(early_january_weather$hour)`. It specifies the time within each day.

6.temp: This variable represents the temperature, likely in degrees Fahrenheit, with values ranging from a minimum of `r min(early_january_weather$temp)` to a maximum of `r max(early_january_weather$temp)`.

7.dewp: The "dewp" variable is likely the dew point temperature, also in degrees Fahrenheit. It ranges from a minimum of `r min(early_january_weather$dewp)` to a maximum of `r max(early_january_weather$dewp)`.

8.humid: This variable represents the humidity level, with values ranging from a minimum of `r min(early_january_weather$humid)` to a maximum of `r max(early_january_weather$humid)`.

9.wind_dir: The "wind_dir" variable likely represents wind direction, measured in degrees. It ranges from `r min(early_january_weather$wind_dir,na.rm=T)` to `r max(early_january_weather$wind_dir,na.rm=T)`, indicating different wind directions. And there are missing values in this variable.

10.wind_speed: This variable represents wind speed, likely measured in some relevant unit (e.g., miles per hour). It ranges from a minimum of `r min(early_january_weather$wind_speed)` to a maximum of `r max(early_january_weather$wind_speed)`.

11.wind_gust: The "wind_gust" variable appears to be related to wind gust speed, with values ranging from a minimum of `r min(early_january_weather$wind_gust,na.rm=T)` to a maximum of `r max(early_january_weather$wind_gust,na.rm=T)`. And there are missing values in this variable.

12.precip: This variable likely represents precipitation, possibly in inches or another relevant unit. It has a range from a minimum of `r min(early_january_weather$precip)` to a maximum of `r max(early_january_weather$precip)`.

13.pressure: The "pressure" variable is likely atmospheric pressure, possibly in millibars or another relevant unit. It ranges from a minimum of `r min(early_january_weather$pressure,na.rm=T)` to a maximum of `r max(early_january_weather$pressure,na.rm=T)`. And there are missing values in this variable.

14.visib: This variable represents visibility, which may be measured in miles or another unit. It includes a quartile statistic with a minimum of `r min(early_january_weather$visib)` and a maximum of `r max(early_january_weather$visib)`.

15.time_hour: This variable seems to indicate the timestamp for each data point, likely in the format "YYYY-MM-DD HH:MM:SS.SS." It specifies the exact time and date of each observation.

* The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

* The mean temperature is about `r round(mean(early_january_weather$temp),2)`.


## A scatterplot of temp (y) vs time_hour (x):

```{r}
# Load the ggplot2 library
library(ggplot2)

# Create the scatterplot
ggplot(early_january_weather, aes(x = hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time-Hour", y = "Temperature", color = "Humidity") +
  theme_minimal()

```

In the scatterplot, we observe distinct temperature patterns throughout the day. During the late night hours, the temperature tends to be at its lowest point. As the morning unfolds and the sun rises, there is a noticeable increase in temperature. The peak of warmth typically occurs around noon, making it the hottest part of the day. Subsequently, as the day progresses, we see a gradual decline in temperature. There is no apparent pattern of humidity from this scatterplot.

```{r}
ggsave("A scatterplot of temp (y) vs time_hour (x).pdf")
```

# Problem 2

## Create a data frame:


提示：目前，要获取数据框中变量的平均值，您需要将变量从数据框中取出。尝试加载 tidyverse 并使用该pull函数。

在某些情况下，您可以显式地将变量从一种类型转换为另一种类型。编写一个代码块，将函数应用于as.numeric 逻辑变量、字符变量和因子变量（请显示该块，但不要显示输出）。会发生什么，为什么？这是否有助于解释当您尝试取均值时会发生什么？

```{r}
library(tidyverse)
df <- tibble(random_sample=rnorm(10),
             logical_vector=random_sample>0,
             character_vector=c("L","O","V","E","Y","O","U","!","!","!"),
             factor_vector<- factor(
               sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE),
               levels = c("Level1", "Level2", "Level3"))
)
```

## Try to take the mean of each variable:

```{r}
mean(pull(df,random_sample))
mean(pull(df,logical_vector))
mean(pull(df,character_vector))
mean(pull(df,`factor_vector <- ...` ))
```
We can get the means of random sample and the logical vector, but we failed in getting means of character vector and factor vector.

## Apply the as.numeric function to the logical, character, and factor variables:

```{r, echo=FALSE}
as.numeric(pull(df,logical_vector))
as.numeric(pull(df,character_vector))
as.numeric(pull(df,`factor_vector <- ...` ))
```

When I convert a logical variable to numeric, TRUE becomes 1, and FALSE becomes 0. 

When I convert a character variable to numeric, it becomes NA.

When I convert a factor variable to numeric, R converts the levels of the factor to their underlying numeric representation. In this case, since the factor levels are "1", "2", and "3," they are converted to 1, 2, and 3, respectively.

Regarding the mean, converting non-numeric variables to numeric using as.numeric can help explain what happens when I try to calculate the mean. When I attempt to calculate the mean of a variable that contains non-numeric values (e.g., characters or factors that cannot be converted to numbers), R returned NA, indicating that the mean cannot be computed due to non-numeric data. Converting such variables to numeric is one way to prepare them for numerical calculations, but I need to ensure that the data can be sensibly interpreted as numbers for the mean calculation to make sense.








